Prospective testing for the prevalence or transience of a shock effect over a set time horizon before it occurs

### 2022-03-30 prevalence_testing/postshocktest2022draft.tex
revision to the manuscript and some revisions of codes

\usepackage{caption}
\usepackage{float}
\usepackage[caption = false]{subfig}
\usepackage{tikz}
\usepackage{multirow}
\usepackage[linesnumbered, ruled,vlined]{algorithm2e}
\usepackage{pdflscape}

@@

\vspace*{0.5cm}\noindent\textcolor{red}{Jilei, explain how the h-ahead forecasts are computed here}

@@

We now motivate a voting method based on the p-values computed in the donor pool.
\textcolor{red}{Jilei, you need to explain what the voting method is, possibly in algorithmic format.}

@@

\begin{table}[H]
	\caption{Results for Conoco Philips ($n=3$), $\mbf{W}^* = (0.183, 0, 0.817)$ from scaled covariates} \label{coptable}
\begin{center}
  \begin{tabular}{cccccccccr}
     $L$  & Model & $\sum_{i=2}^4 w_i^* I(a_i^1 > a_i^2)$ & $p_1$ &  $|\hat{p}-p_1|$ & Vote (Correct?) & weighted Vote (Correct?)   \\
     \hline 
     7 & $\mc{M}_0$  & \multirow{2}{*}{$0.817$} & 1  & 0 & 0 (Yes) &0 (Yes)  \\      
     7 & $\mc{M}$  &  & 1 & $0$   & 0 (Yes) &0 (Yes)   \\[.2cm]
     15 & $\mc{M}_0$ & \multirow{2}{*}{$0.817$}  & 1   & $0.82$ & 0 (Yes) &1 (No)    \\
     15 &  $\mc{M}$ & & 1 & 0 &0 (Yes)  &0 (Yes)  \\[.2cm]
     30 &  $\mc{M}_0$ & \multirow{2}{*}{$1$}  & 1   & $0.82$ & 0 (Yes) &1 (No)   \\
     30 &  $\mc{M}$ &  & 1  & 0 &0 (Yes) & 0 (Yes)  
  \end{tabular}
\end{center}	
\end{table}

@@

\begin{table}[H]
	\caption{Results for Month-on-Month Change in Log Nonfarm Payrolls (Seasonally Adjusted) ($n=3$), $\mbf{W}^* = (0, 0.278, 0.722)$ from scaled covariates} \label{uemtable}
\begin{center}
  \begin{tabular}{ccccccccr}
      Model & $\sum_{i=2}^4 w_i^* I(a_i^1 > a_i^2)$  & $p_1$ &  $|\hat{p}-p_1|$ & Vote (Correct?) & weighted Vote (Correct?)   \\
     \hline 
     $\mc{M}_0$  & \multirow{2}{*}{0.722}& 0  & 1 & 1 (No) &1 (No)  \\      
      $\mc{M}$ ($q_1=q_2=1$)  & & 0.470 & $0.146$   & 0 (Yes) &0 (Yes)   \\[.2cm]
  \end{tabular}
\end{center}	
\end{table}

>>>>

\usepackage{caption}
\usepackage{float}
\usepackage[caption = false]{subfig}
\usepackage{tikz}
\usepackage{multirow}
\usepackage[linesnumbered, ruled,vlined]{algorithm2e}
\usepackage{pdflscape}
\usepackage{algorithm2e}

@@

\textcolor{red}{Next, we define the $h$-step forecast for $\mc{M}$, which plays an essential role in the framework of \citet{quaedvlieg2021multi}. Denote $h$-step forecast for $y_{i,t}$ by $\hat{y}_{i,t}^h$. Let the OLS estimate for
\begin{align*}
	\{(\eta_i, \alpha_i, \phi_{i,j_1}, \bs{\theta}_{i,j_2}, \tilde{\phi}_{i,j_1}, \tilde{\bs{\theta}}_{i,j_2}) \colon i = 2, \ldots, n+1, j_1 = 1, \ldots, q_1, j_2 = 1, \ldots, q_2\}
\end{align*}
 be 
 \begin{align*}
 	\{(\hat{\eta}_i, \hat{\alpha}_i, \hat{\phi}_{i,j_1}, \hat{\bs{\theta}}_{i,j_2}, \hat{\tilde{\phi}}_{i,j_1}, \hat{\tilde{\bs{\theta}}}_{i,j_2}) \colon i = 2, \ldots, n+1, j_1 = 1, \ldots, q_1, j_2 = 1, \ldots, q_2\}.
 \end{align*}
Based on the training data $\{(\mbf{x}_{i, t}, y_{i,t}) \colon i = 2, \ldots, n+1, t = 1, \ldots, T_i\}$, for $h = 1, \ldots, H$, the $h$-step forecast $\hat{y}_{i,t}^h$ is defined as
 \begin{align*}
 	\hat{y}_{i,t}^h &= \left(\hat{\eta}_i + \sum_{j=1}^{q_1}\hat{\phi}_{i,j}\hat{y}^{h-j}_{i, t-j} + \sum_{j=0}^{q_2-1}\mbf{x}_{i,t-j}\hat{\bs{\theta}}_{i,j+1}\right)(1 - D_{i,t}) + f(\hat{\mathcal{F}}_{i,t},\hat{\alpha}_i)D_{i,t} ,\\[.2cm]
  \; f(\hat{\mc{F}}_{i,t},\hat{\alpha}_i ) &= \hat{\alpha}_i +  \sum_{j=1}^{q_{1}}\hat{\tilde{\phi}}_{i,j} \hat{y}^{h-j}_{i, t-j}+ \sum_{j=0}^{q_2-1}\mbf{x}_{i,t-j}\hat{\tilde{\bs{\theta}}}_{i,j+1},
 \end{align*}
 where it is allowed that $t> T_i$, and we set $\hat{y}^{s}_{i, t}=y_{i,t}$ for $t \leq T_i$ and $s\leq 0$. This definition is in line with  that of  the iterated $h$-step ahead forecast  in the time series literature.}

@@

We now motivate a voting method and a weighted voting method based on the p-values computed in the donor pool and \textcolor{red}{the algorithms are described in Algorithm \ref{voting}. There are a couple of details that are worth noting. First, for $t = T_i+1$ and $i \geq 2$, we used to the methodology of \cite{lin2021minimizing} to compute point forecast for $\hat{y}_{i,t}^{2,h}$. Note that for $t = T_i+1$, using ordinary least square conditional forecast yields $\hat{y}_{i,t}^{2,h}=  \hat{y}_{i,t}^{1,h}$ as those two forecast just differ by shock information, which is not available at this time point. We make such adjustment for the reason that  the method of  \cite{lin2021minimizing} is generally more likely to perform better than the ordinary forecast under certain conditions. Second, notice that we evaluate forecast comparison for $t = K_i + H+ \max\{q_1, q_2-1\} + 1, \ldots, T_i$ with time length smaller than $T_i$. It is because the framework of \cite{quaedvlieg2021multi} needs training sample, which implicitly requires users to feed the algorithm with moderately large dataset for a more credible analysis. }

\vspace{.5cm}
\begin{algorithm}[H]
\SetAlgoLined \label{voting}

\SetKwInOut{Input}{Input}
\Input{$B, \ell $ --  bootstrap sample size, the  block size,   \\ 
$\gamma$ -- bandwidth parameter in heteroskedasticity and autocorrelation  consistent covariance \\ 
	\quad \quad matrix  estimation.\\ 
$\alpha$ -- significance level\\$\{(y_{i,t}, \mbf{x}_{i,t})\colon i = 2,\ldots, n+1, t = 0, \ldots, T_i\}$ -- the data\\ $\{T_i^* \colon i = 1, \ldots, n+1\}$ -- the time point just before the shock\\
$\{K_i \colon i = 2, \ldots, n+1\}$  -- training sample size for $h$-step forecast for different time series \\
$q_1, q_2$ -- user-specified parameters in $\mc{M}$ \\
$H$ -- maximum horizon 
}

\KwResult{(1) synthetic weights $\mbf{W}^*$, (2)  $\hat{p}_1$, and (3) decision based on voting and weighted voting}

  \For{$i = 2:(n+1)$}{
  	\If{$i > 2$}{
  	Compute $\hat{\alpha}_{\rm wadj}$ based on \cite{lin2021minimizing} with $\{T_j^* \colon j = 2, \ldots, i-1\}$ and $\{(y_{j,t}, \mbf{x}_{j,t})\colon j= 2,\ldots, i-1, t = 0, \ldots, T_j\}$
  	}

 	\For{$h = 1, \ldots, H$}{
 		\For{$t = K_i + H+ \max\{q_1, q_2-1\} + 1, \ldots, T_i$}{
 		Compute $\hat{y}_{i,t}^{1, h}$ and $\hat{y}_{i,t}^{2, h}$ based on OLS estimation of $\mc{M}$ with $\{T_i^* \colon i = 1, \ldots, n+1\}$ and   training data $\{(y_{i,t}, \mbf{x}_{i,t})\colon  t =  t-h- K_i +1, \ldots, t-h\}$, where we further need the set of lagged response $\{y_{i,t}\colon t = t-h-K_i- \max\{q_1, q_2-1\}+1, t-h-K_i\}$.

 		\If{$t-h = T_i^*$, $i\geq 3$, and $h =1$}{
 		$\hat{y}_{i,t}^{2, h}= \hat{y}_{i,t}^{2, h} + \hat{\alpha}_{\rm wadj}$
 		}
 		Compute the squared error loss $l_{t,h}^1$ based on $y_{i, t}$
 		 and $\hat{y}_{i,t}^{1, h}$\\
 		 Compute the squared error loss $l_{t,h}^2$ based on $y_{i, t}$
 		 and $\hat{y}_{i,t}^{2, h}$
 		}
 	}
 	Construct the loss differential matrix with element $l_{t,h}^2-l_{t,h}^1$ at $t$th row and $h$th column \\
 	Conduct multiple horizon forecast comparison test of \cite{quaedvlieg2021multi} on the loss differential matrix $\{l_{t,h}^2-l_{t,h}^1\}_{t,h}$ with parameters $\ell, B, \gamma$ to obtain forecast comparison $p$-value $\hat{p}_i$\\
  }

 	Compute synthetic weights $\mbf{W}^*= (w_2^*, \ldots, w_{n+1}^*)$ based on $\{\mbf{x}_{i, T_i^*+1}\colon i = 1, \ldots, n+1\}$ \\
 	Compute the vote $V= I\Big\{n^{-1}\sum_{i=2}^{n+1}I(\hat{p}_i \leq  \alpha) \geq 0.5\Big\}$ \\
 	Compute the weighted vote $V^*= I\Big\{ \sum_{i=2}^{n+1}w_i^*I(\hat{p}_i \leq  \alpha) \geq 0.5\Big\}$

 \caption{Algorithm for computing $\hat{p}_1$, weighted voting, and $\mbf{W}^*$}\label{Bu}
\end{algorithm}

@@

\begin{table}[H]
	\caption{Results for Conoco Philips ($n=3$), $\mbf{W}^* = (0.183, 0, 0.817)$ from scaled covariates} \label{coptable}
\begin{center}
  \begin{tabular}{cccccccccr}
     $L$  & Model & $\sum_{i=2}^4 w_i^* I(a_i^1 > a_i^2)$ & $p_1$ &  $|\hat{p}-p_1|$ & Vote (Correct?) & weighted Vote (Correct?)   \\
     \hline 
     7 & $\mc{M}_0$  & \multirow{2}{*}{$0.817$} & 1  & 0 & 0 (Yes) &0 (Yes)  \\      
     7 & $\mc{M}$  &  & 1 & $0$   & 0 (Yes) &0 (Yes)   \\[.2cm]
     15 & $\mc{M}_0$ & \multirow{2}{*}{$0.817$}  & 1   & $0.817$ & 0 (Yes) &1 (No)    \\
     15 &  $\mc{M}$ & & 1 & 0 &0 (Yes)  &0 (Yes)  \\[.2cm]
     30 &  $\mc{M}_0$ & \multirow{2}{*}{$1$}  & 1   & $0.817$ & 0 (Yes) &1 (No)   \\
     30 &  $\mc{M}$ &  & 1  & 0 &0 (Yes) & 0 (Yes)  
  \end{tabular}
\end{center}	
\end{table}

@@

\begin{table}[H]
	\caption{Results for Month-on-Month Change in Log Nonfarm Payrolls (Seasonally Adjusted) ($n=3$), $\mbf{W}^* = (0, 0.278, 0.722)$ from scaled covariates} \label{uemtable}
\begin{center}
  \begin{tabular}{cccccccccr}
   $L$  &  Model & $\sum_{i=2}^4 w_i^* I(a_i^1 > a_i^2)$  & $p_1$ &  $|\hat{p}-p_1|$ & Vote (Correct?) & weighted Vote (Correct?)   \\
     \hline 
     \multirow{2}{*}{ $3$} &  $\mc{M}_0$  & \multirow{2}{*}{ 0}& 1  & 0 & 0 (Yes) &0 (Yes)  \\      
      & $\mc{M}$ ($q_1=q_2=1$)  & & 0.070 & $0.179$   & 0 (Yes) &1 (No)   \\[.2cm]
     \multirow{2}{*}{ $6$} &  $\mc{M}_0$  & \multirow{2}{*}{ 0}& 1  & 0 & 0 (Yes) &0 (Yes)  \\      
      & $\mc{M}$ ($q_1=q_2=1$)  & & 0.265 & $0.498$   & 0 (Yes) &0 (Yes)   \\[.2cm]
  \multirow{2}{*}{ $12$} &  $\mc{M}_0$  & \multirow{2}{*}{0.722}& 0  & 1 & 1 (No) &1 (No)  \\      
      & $\mc{M}$ ($q_1=q_2=1$)  & & 0.470 & $0.146$   & 0 (Yes) &0 (Yes)   \\[.2cm]
       \multirow{2}{*}{ $18$} &  $\mc{M}_0$  & \multirow{2}{*}{0}& 0.670  & 0.330 & 0 (Yes) & 0 (Yes)  \\      
      & $\mc{M}$ ($q_1=q_2=1$)  & & 1 & $0$   & 0 (Yes) &0 (Yes)   \\[.2cm]
  \end{tabular}
\end{center}	
\end{table}
